---
author: "Kaleb Crisci"
date: "10/31/2019"
title: "Class Schedules"
output: html_notebook
---

# Introduction
This is the class schedule for 2 different semesters and 2 different departments at Chico State. We use web-scraping to pull information off of 4 different pages and combine them into one table.

# Get Data
First, we load the libraries we will be using. 

```{r, results='hide', message=FALSE}
include <- function(library_name){
  if( !(library_name %in% installed.packages()) )
    install.packages(library_name) 
  library(library_name, character.only=TRUE)
}
include("tidyverse")
include("dplyr")
```

This is the function that will pull several columns of data from a given URL. Each URL contains the same class names, so this function will work on any of the Chico State class schedules.  
The first step is to read the html from the URL using the *read_html* function.  
Then, we pull only the information that we want from the html variable. The *html_nodes* function takes in the html variable, and the class, id, or tag name that we are trying to get. Then, we have to convert this data into text format using *html_text* function. Without this last step, the data will be represented as objects.
We also use the pattern matching function *str_extract* to find the year and the semester from the page, and insert this information into the table.  
Finally, we put the data that we want into a tibble, and return the created table.
```{r}
read_class_schedule <- function(url) {
  html <- read_html(url)
  subjects <- html %>% html_nodes("td.subj") %>% html_text()
  class_num <- html %>% html_nodes("td.cat_num") %>% html_text()
  class_number <- paste(subjects, class_num)
  section_number <- html %>% html_nodes("td.sect") %>% html_text()
  course_title <- html %>% html_nodes("td.title") %>% html_text()
  units <- html %>% html_nodes("td.units") %>% html_text()
  days <- html %>% html_nodes("td.days") %>% html_text()
  instructor <- html %>% html_nodes("td.Instructor") %>% html_text()
  enrollment <- html %>% html_nodes("td.enrtot") %>% html_text()
  pattern_year <- "20[0-9]{2}"
  string_year <- html %>% html_nodes(".returntoindexlink") %>% html_text()
  string_semester <- html %>% html_nodes(".returntoindexlink") %>% html_text()
  pattern_semester <- "Winter|Spring|Summer|Fall"
  year <- str_extract(string_year, pattern_year)
  semester <- str_extract(string_semester, pattern_semester)
  table <- tibble(class_number, section_number, course_title, units, days, instructor, enrollment, semester, year)
  return(table)
}
```

Using the above function, we get the information from 2 different departments and 2 different semesters, and put it into separate tables.
```{r}
CSCI_Spring_2019 <- read_class_schedule("http://ems.csuchico.edu/APSS/schedule/spr2019/CSCI.shtml")

CSCI_Spring_2020 <- read_class_schedule("http://ems.csuchico.edu/APSS/schedule/spr2020/CSCI.shtml")

Math_Spring_2019 <- read_class_schedule("http://ems.csuchico.edu/APSS/schedule/spr2019/MATH.shtml")

Math_Spring_2020 <- read_class_schedule("http://ems.csuchico.edu/APSS/schedule/spr2020/MATH.shtml")

```

Next, we combine all the tables into one table
```{r}
full_schedule <- rbind(CSCI_Spring_2019, CSCI_Spring_2020, Math_Spring_2019, Math_Spring_2020)
```

